The \project{UNRAVE} catalog

### 2016-08-15 article/unrave.tex
Formatting, etc

@@

\begin{abstract}
On 14 September 2016 the \project{Gaia} mission will release positions, proper motions, and parallaxes for about two million stars.  Most studies intending to make use of those data would benefit enormously from stellar chemical abundances.  The RAdial Velocity Experiment (\project{RAVE}) survey has acquired spectra for approximately 290,000 stars in common with the first \project{Gaia} data release, constituting the largest overlap of any stellar spectroscopic sample.  Here we perform an independent analysis of the \project{RAVE} spectra using a new non-parametric implementation of \thecannon\ that employs prior probabilities on atomic line formation and stellar astrophysical parameters.  We deliver effective temperature $\teff$, surface gravity $\logg$, and chemical abundances of up to seven elements (Mg, Al, Si, Ca, Ti, Fe, Ni) for \Nstars\ stars.  We validate our results internally from repeat visits, and externally against existing high-resolution spectroscopic surveys.  The typical precision in chemical abundances is $X.XX$~dex.  
\end{abstract}

@@

% When did RAVE observe?
% Where from

% target selection.
% wavelength range

% How many data releases
% What was in previous data releases?

% Data reduction
% Normalization
% Flux errors

>>>>

% Look for \stub{}s. If you can expand it, do so!

@@

\begin{abstract}
On 14 September 2016 the \project{Gaia} mission will release positions, proper 
motions, and parallaxes for about two million stars.  Most studies intending to
make use of those data would benefit enormously by coupling that astrometry with
stellar chemical abundances.  The RAdial Velocity Experiment (\project{RAVE}) 
survey has acquired spectra for approximately 290,000 stars in common with the 
first \project{Gaia} data release, constituting the largest overlap of any 
stellar spectroscopic sample.  Here we perform an independent analysis of the 
\project{RAVE} spectra using a new non-parametric implementation of \thecannon\ 
that employs prior probabilities on atomic line formation and stellar 
astrophysical parameters.  We deliver effective temperature $\teff$, surface 
gravity $\logg$, and chemical abundances of up to seven elements (Mg, Al, Si, 
Ca, Ti, Fe, Ni) for \Nstars\ stars.  We validate our results internally from 
repeat visits, and externally against existing high-resolution spectroscopic 
surveys.  The typical precision in chemical abundances is $X.XX$~dex.  
\end{abstract}

@@
